---
title: "NC State Scouting Report"
author: "VT Softball Analytics Team"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: "left=1.5cm,right=1.5cm,top=1.5cm,bottom=1.5cm"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 10)
```

```{r, warning = FALSE, message = FALSE}
source('plot_functions.R')
library(dplyr)
library(kableExtra)

# Import and clean data
### MUST CHANGE FOLDER NAME - FOLDER SHOULD CONTAIN ONLY CSV FILES FOR SPECIFIC TEAM
files = list.files(path = "./NCST", pattern = "*.csv", full.names = T)
games = lapply(files, read.csv, stringsAsFactors = FALSE)
games = lapply(games, select_columns)
games = bind_rows(games)
games = clean_data(games)

# Select team - using one of the following two lines of code
### MUST MANUALLY CHECK WHICH ONE TO USE TO GET THE RIGHT TEAM 
#team = games$Team.at.Bat[1]
team = games$Team.in.Field[1]

### SOMETIMES XOS GIVES AN ODD GAME NAME - CHECK THIS IN THE TABLE AND MANUALLY ADJUST ANY ODD ONES
# table(games$Name)
games$Name[which(games$Name == '202003071615050')] = 'ND vs NC State GM 1'
games$Name[which(games$Name == '202003110754550')] = 'Norfolk State vs NC State'
```

This report includes data from the following games:

```{r}
# Table of games
temp_table = data.frame(Included.Games = unique(games$Name))
kable(temp_table) %>%
  kable_styling()
```

The game data include the following pitchers.  If the pitcher handedness is blank, we simply did not have their hand strength listed in the data.

```{r}
# Table of pitchers
pitchers = unique(games$Pitcher[which(games$Team.in.Field == team)])
hand = c()
at_bats = c()
for (i in 1:length(pitchers)){
  hand = c(hand, games$Pitcher.Strength[which(games$Pitcher == pitchers[i])[1]])
  at_bats = c(at_bats, sum(games$Pitcher == pitchers[i] & games$Count == '0-0'))
}
kable(data.frame(name = pitchers, handedness = hand, at.bats = at_bats), align = c('l','c','c')) %>%
  kable_styling()
```

The game data include the following batters.  Note, plots are only provided for batters that had at least five at bats.

```{r}
# Table of batters
batters = unique(games$Batter[which(games$Team.at.Bat == team)])
hand = c()
at_bats = c()
for (i in 1:length(batters)){
  hand = c(hand, games$Batter.Strength[which(games$Batter == batters[i])[1]])
  at_bats = c(at_bats, sum(games$Batter == batters[i] & games$Count == '0-0'))
}
kable(data.frame(name = batters, handedness = hand, at.bats = at_bats), align = c('l','c','c')) %>%
  kable_styling()
```

# Changeups by Pitcher

We do not have any data on which pitches were changeups in these games.

```{r, fig.height = 5, eval = FALSE}
### IF CHANGEUP DATA IS AVAILABLE, CHANGE "eval = FALSE" to TRUE in the line above
par(mar = c(8, 4, 4, 2), mfrow = c(1,2))
changeup_barplot(games, team)
```

# Pitcher Spray Charts - `r pitchers[1]`

```{r, fig.width = 10, fig.height = 5.5}
### MUST MANUALLY CHECK HOW MANY PITCHERS THERE ARE, AND COPY THIS "PITCHER SPRAY CHART"
### SECTION THE APPROPRIATE AMOUNT OF TIMES WHILE CHANGING INDEX
pitch_scatterplot(games, pitchers[1])
```

# Pitcher Spray Charts - `r pitchers[2]`

```{r, fig.width = 10, fig.height = 5.5}
pitch_scatterplot(games, pitchers[2])
```

# Pitcher Spray Charts - `r pitchers[3]`

```{r, fig.width = 10, fig.height = 5.5}
pitch_scatterplot(games, pitchers[3])
```

# Pitch Result by Count - Pitchers

```{r, eval = TRUE}
make_barplot(games, team, type = 'pitcher')
```

# Pitch Result by Count - Batters

```{r, eval = TRUE}
make_barplot(games, team, type = 'batter')
```

# Bunt Analysis

This team bunted `r sum(games$Team.at.Bat == team & games$Plot.Result == 'BUNT ATTEMPT') ` times in `r length(unique(games$Name))` games.  Details of the bunts are given in the following table.

```{r}
bunts = games[which(games$Team.at.Bat == team & games$Plot.Result == 'BUNT ATTEMPT'),]
kable(data.frame(game = bunts[,'Name'], batter = bunts[,'Batter'],
                 count = bunts[,'Count'], outs = bunts[,'Outs'],
                 result = bunts[,'Strike.Type']), align = c('l', rep('c', 4))) %>%
  kable_styling()
```

# Steal Analysis

```{r}
games$Stolen.Base.Lead[which(is.na(games$Stolen.Base.Lead))] = ''
games$Caught.Stealing[which(is.na(games$Caught.Stealing))] = ''
```

In `r length(unique(games$Name))` games, this team had `r sum(games$Team.at.Bat == team & games$Stolen.Base.Lead != '')` successful steals and was caught stealing `r sum(games$Team.at.Bat == team & games$Caught.Stealing != '')` times.  Details of the steals are given in the following table.

```{r}
steals = games[which(games$Team.at.Bat == team & (games$Stolen.Base.Lead != '' | games$Caught.Stealing != '')),]
df = data.frame(game = steals[,'Name'], stealer = steals[,'Stolen.Base.Lead.Runner'],
                 count = steals[,'Count'], outs = steals[,'Outs'],
                 base.stolen = steals[,'Stolen.Base.Lead'],
                 caught.stealing = steals[,'Caught.Stealing'])
df$stealer = as.character(df$stealer)
df$stealer[which(df$caught.stealing == '2B')] = steals$Base.Runner.1st.Base[which(steals$Caught.Stealing == '2B')]
df$stealer[which(df$caught.stealing == '3B')] = steals$Base.Runner.2nd.Base[which(steals$Caught.Stealing == '3B')]
kable(df, align = c('l', rep('c', 6))) %>%
  kable_styling()
```




